### 2017-07-07 motivation.tex
Edits.

This simple characterization of SI isolation allows us to verify the
consistency conditions associated with the \C{new\_order} transaction.
First, since the database doesn't change ($\Delta' = \Delta$) during
the execution of the transaction's body, we can reason about
\C{new\_order} as though it executed in complete isolation until its
commit point, leading to a verification process similar to what would
been applied when reasoning about serializability.  When
\C{new\_order} finishes execution, but before it commits, the SI
axiomatization shown above requires us to consider global state
transitions $\stg \longrightarrow \stg'$ that do not include changes
to the records ($\stl$) written by \C{new\_order}, i.e.,
$\forall(x\in\delta).~\Delta'(x) = \Delta(x)$. Since concurrent
\C{new\_order} transactions that write to the same C{District} record
modify the record by incrementing its \C{d\_next\_o\_id} field,
their transitions do not satisfy the necessary condition imposed by
the SI axiomatization, allowing us to rightfully ignore their
interference. This leaves the interference due to concurrent
\C{new\_order} transactions that write to a different district record. 
Fortunately, such interference does not prompt \C{new\_order} to
violate the invariant, which can be established by reasoning on the
similar lines as concurrent program logics, such as the Rely-Guarantee
logic.

>>>>

This simple characterization of SI isolation allows us to verify the
consistency conditions associated with the \C{new\_order} transaction.
First, since the database doesn't change ($\Delta' = \Delta$) during
the execution of the transaction's body, we can reason about
\C{new\_order} as though it executed in complete isolation until its
commit point, leading to a verification process similar to what would
been applied when reasoning about serializability.  When
\C{new\_order} finishes execution, but before it commits, the SI
axiomatization shown above requires us to consider global state
transitions $\stg \longrightarrow \stg'$ that do not include changes
to the records ($\stl$) written by \C{new\_order}, i.e.,
$\forall(x\in\delta).~\Delta'(x) = \Delta(x)$. Since concurrent
\C{new\_order} transactions that write to the same \C{District} record
modify the record by incrementing its \C{d\_next\_o\_id} field, their
transitions do not satisfy the necessary condition imposed by the SI
axiomatization, allowing us to rightfully ignore their interference.
This leaves the interference due to concurrent \C{new\_order}
transactions that write to a different district record.  Fortunately,
such interference does not prompt \C{new\_order} to violate the
invariant, which can be established by adopting a reasoning similar to
the one used on concurrent program logics, such as the Rely-Guarantee
logic, customized for the database programs.
